---
title: "Unwilling / unable: 3D tracking data processing"
author: "Christoph Voelter"
date: "21/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lme4)
library(summarytools)
library(glmmTMB)
library(car)



```


### Read all csv files in folder

```{r}
demo.data <- read.csv(file = "data/unwilling_unable_demographics.csv") %>%
  select(-comments.dogs)%>%
  rename(subject=CDL.name)

view(dfSummary(demo.data))

object.data <- read.csv(file = "data/object_data.csv")

#interest area around owner chair
chair_window_ia_xr <- object.data$x[object.data$name=="chair_r1"]+1000
chair_window_ia_xl <- object.data$x[object.data$name=="chair_l1"]-1000
chair_window_ia_yl <- object.data$y[object.data$name=="chair_l1"]-1000
chair_window_ia_yh <- 6050 #boundary of the room
size_chair_IA <- (chair_window_ia_yh-chair_window_ia_yl) * (chair_window_ia_xr-chair_window_ia_xl)
chair_window_centre_x <- (object.data$x[object.data$name=="chair_r2"] + object.data$x[object.data$name=="chair_l1"])/2
chair_window_centre_y <- (object.data$y[object.data$name=="chair_l1"] + object.data$y[object.data$name=="chair_l2"])/2

```

```{r}
read_plus <- function(flnm) {
    read_csv(flnm) %>% 
        mutate(filename = flnm)
}

xdata <-
    list.files(path = "./data/raw/",
               pattern = "*.csv", 
               full.names = T) %>% 
    map_df(~read_plus(.))%>%
  separate(filename,  into=c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,"subject","condition", NA, NA, NA), sep = "_")%>% #add info from filenames
  select(-frame_number, -"_cameras", -frame_timestamp, -type)

summary(xdata)
xdata%>%filter(!is.na(name))%>%group_by(subject, condition)%>%summarise(min(x))
levels(as.factor(xdata$subject))
levels(as.factor(xdata$name))
levels(as.factor(xdata$condition))
levels(as.factor(xdata$subject_condition))


```


```{r}
trial.duration.data <- read.csv(file = "data/scoringproject_46_unwilling_unable_test_trials.csv")%>%
  select(Start_Frame, Stop_Frame, subject, condition, trial)


xx<-trial.duration.data%>%
  pivot_longer(cols=Start_Frame:Stop_Frame, values_to="frame_count", names_to="start_stop")%>%
  group_by(subject, condition, trial)%>%
  complete(frame_count=seq(from=min(frame_count, na.rm=TRUE), to=max(frame_count, na.rm=TRUE)))

```


### Plot all raw data (separate plots)
```{r eval=FALSE}
subjects = unique(xdata$subject)
names = unique(xdata$name)
conditions =unique(xdata$condition)
subject_plots = list()

for(name_ in names){
for(condition_ in conditions){
for(subject_ in subjects) {
  subject_plots[[subject_]] = 
    ggplot(xdata %>% filter(subject == subject_ & name == name_ & condition == condition_), aes(x=x, y=y)) +
    geom_path(alpha=0.15) + 
    geom_point(alpha=0.15) +
       annotate("rect", xmin=object.data$x[object.data$name=="obstacle_l1"], xmax=object.data$x[object.data$name=="obstacle_r1"], ymin=object.data$y[object.data$name=="obstacle_r2"],ymax=object.data$y[object.data$name=="obstacle_r1"], fill="#E8E288", alpha=0.9)+
    annotate("rect", xmin=object.data$x[object.data$name=="chair_l1"], xmax=object.data$x[object.data$name=="chair_r1"], ymin=object.data$y[object.data$name=="chair_r1"],ymax=object.data$y[object.data$name=="chair_r2"], fill="#9BBEC7", alpha=0.9)+
    theme(axis.text.x = element_text(angle = 90)) + 
    theme_bw()+ ggtitle(paste0(condition_, ": ", subject_, ": ",name_ )) + 
    ylab("y") + xlab("x") + 
    ylim(0, 6050) + xlim(0, 7300) + 
    theme(plot.title = element_text(size = 24, face = "bold", hjust=0.5), axis.title.x = element_text(size = 16, face = "bold"), axis.title.y = element_text(size = 16, face = "bold"))
  
  print(subject_plots[[subject_]])
  
  ggsave(subject_plots[[subject_]], path="graphics/raw_plots", file=paste0("plot_", subject_, "_", condition_, "_", name_,".png"), width = 20, height = 15, units = "cm", dpi=300)
}
}
}
```


### Filtered, interpolated, and smoothed data: all keypoints in one plot 

#### calculate distance

```{r}
library(zoo)

average_coordinates<-xdata %>%
  inner_join(xx)%>%
    group_by(subject, condition,trial, frame_count)%>%
  filter(x<7300 & x >0)%>% filter(z<1500)%>%filter(y<6050 & y>0)%>% #filter out unrealistic values
  summarise(average_x=mean(x),average_y=mean(y), average_z=mean(z))%>%
  select(subject, condition, trial, frame_count, average_x, average_y, average_z)

xdata.int<-xdata%>%
  inner_join(xx)%>%
  group_by(subject,condition, trial, name)%>%
  inner_join(average_coordinates)%>%
  filter(x<7300 & x >0)%>% filter(z<1500)%>%filter(y<6050 & y>0)%>% #filter out unrealistic values
  filter(abs(x-average_x)<1000 & abs(y-average_y)<1000 & abs(z-average_z)<1000)%>% #filter out values that deviate from average value
  filter((abs(x-lag(x))<1500 & abs(y-lag(y))<1500 & abs(z-lag(z))<1500 & abs(x-lead(x))<1500 & abs(y-lead(y))<1500 & abs(z-lead(z))<1500))%>% #filter out jumps of 0.5m and more
  complete(frame_count=seq(from=min(frame_count, na.rm=TRUE), to=max(frame_count, na.rm=TRUE)))%>% #add all missing frames
  mutate(x_approx = na.approx(x,  na.rm = TRUE),y_approx = na.approx(y,  na.rm = TRUE), z_approx = na.approx(z,  na.rm = TRUE))%>% #first linear interpolation
  filter((abs(x_approx-lag(x_approx))<200 & abs(y_approx-lag(y_approx))<200 & abs(z_approx-lag(z_approx))<200 & abs(x_approx-lead(x_approx))<200 & abs(y_approx-lead(y_approx))<200 & abs(z_approx-lead(z_approx))<200))%>% #filter out jumps of 20cm and more between two consecutive frames
  complete(frame_count=seq(from=min(frame_count, na.rm=TRUE), to=max(frame_count, na.rm=TRUE)))%>% #add all missing frames
    mutate(x_approx = na.approx(x_approx, na.rm = TRUE),y_approx = na.approx(y_approx,  na.rm = TRUE), z_approx = na.approx(z_approx,  na.rm = TRUE))%>% # second linear interpolation
  filter((abs(x_approx-lag(x_approx))<200 & abs(y_approx-lag(y_approx))<200 & abs(z_approx-lag(z_approx))<200 & abs(x_approx-lead(x_approx))<200 & abs(y_approx-lead(y_approx))<200 & abs(z_approx-lead(z_approx))<200))%>% #filter out jumps of 20cm and more between two consecutive frames
  complete(frame_count=seq(from=min(frame_count, na.rm=TRUE), to=max(frame_count, na.rm=TRUE)))%>% #add all missing frames
    mutate(x_approx = na.approx(x_approx, na.rm = TRUE),y_approx = na.approx(y_approx,  na.rm = TRUE), z_approx = na.approx(z_approx,  na.rm = TRUE))%>% # third linear interpolation
  filter((abs(x_approx-lag(x_approx))<200 & abs(y_approx-lag(y_approx))<200 & abs(z_approx-lag(z_approx))<200 & abs(x_approx-lead(x_approx))<200 & abs(y_approx-lead(y_approx))<200 & abs(z_approx-lead(z_approx))<200))%>% #filter out jumps of 20cm and more between two consecutive frames
  complete(frame_count=seq(from=min(frame_count, na.rm=TRUE), to=max(frame_count, na.rm=TRUE)))%>% #add all missing frames
    mutate(x_approx = na.approx(x_approx, na.rm = TRUE),y_approx = na.approx(y_approx,  na.rm = TRUE), z_approx = na.approx(z_approx,  na.rm = TRUE))%>% # 4th linear interpolation
  mutate(x_approx_roll = zoo::rollmean(x_approx, k = 3, fill = NA), y_approx_roll = zoo::rollmean(y_approx, k = 3, fill = NA),z_approx_roll = zoo::rollmean(z_approx, k = 3, fill = NA))%>% #rolling average
  mutate(x1=lead(x_approx_roll), y1=lead(y_approx_roll), z1=lead(z_approx_roll))%>% #add xyz coordinates of next frame
  mutate(distance=sqrt((x1-x_approx_roll)^2+(y1-y_approx_roll)^2+(z1-z_approx_roll)^2))%>%
  mutate(duration_chair_owner=as.numeric(ifelse(x_approx_roll>= chair_window_ia_xl & x_approx_roll<= chair_window_ia_xr & y_approx_roll>= chair_window_ia_yl & y_approx_roll<= chair_window_ia_yh, 1, 0)))%>%
  mutate(distance_chair_owner= sqrt((chair_window_centre_x-x_approx_roll)^2+(chair_window_centre_y-y_approx_roll)^2))%>%
  inner_join(demo.data)
```

```{r}
xdata.int<-xdata.int%>%mutate(subject_condition=paste(subject, condition,trial, sep="_"))
subjects = unique(xdata.int$subject)
names = unique(xdata.int$name)
conditions =unique(xdata.int$condition)
subject_conditions =unique(xdata.int$subject_condition) #"Allegro2_blocked_1"

library(zoo)
subject_dfs = list()
subject_average_dfs = list()
subject_plots = list()

for(subject_condition_ in subject_conditions){


subject_dfs[[subject_condition_]]<-xdata.int %>% filter(subject_condition == subject_condition_)%>%
  group_by(name)
 
  subject_plots[[subject_condition_]] = 
    ggplot(subject_dfs[[subject_condition_]], aes(x=x_approx_roll, y=y_approx_roll)) +
    geom_path(alpha=0.1) + 
    geom_point(alpha=0.02) +
       annotate("rect", xmin=object.data$x[object.data$name=="obstacle_l1"], xmax=object.data$x[object.data$name=="obstacle_r1"], ymin=object.data$y[object.data$name=="obstacle_r2"],ymax=object.data$y[object.data$name=="obstacle_r1"], fill="#E8E288", alpha=0.9)+
    annotate("rect", xmin=object.data$x[object.data$name=="chair_l1"], xmax=object.data$x[object.data$name=="chair_r1"], ymin=object.data$y[object.data$name=="chair_r1"],ymax=object.data$y[object.data$name=="chair_r2"], fill="#9BBEC7", alpha=0.9)+
    theme(axis.text.x = element_text(angle = 90)) + 
    theme_bw()+ ggtitle(subject_condition_) + 
    facet_wrap(~name)+ #creates facets
    ylab("y") + xlab("x") + 
    ylim(0, 6050) + xlim(0, 7300) +  
    theme(plot.title = element_text(size = 24, face = "bold", hjust=0.5), axis.title.x = element_text(size = 16, face = "bold"), axis.title.y = element_text(size = 16, face = "bold"))
  
  print(subject_plots[[subject_condition_]])
  
  ggsave(subject_plots[[subject_condition_]], path="./graphics/interpolated2", file=paste0("plot_facets_interpolated_", subject_condition_, ".png"), width = 40, height = 30, units = "cm", dpi=300, scale=0.7)
  
}

```






```{r}
xdata.saved<-xdata.int%>%
  rename(keypoint=name)%>%
  select(-oid, -date, -x1, -y1 , -z1)
write.csv(xdata.saved, file = "data/dog_tracking_data_interpolated.csv")


save.image("unwilling_unable_3D_workspace.RData")
```


Calculate the area covered by the dog (based on grid with cells of 50 x 50 cm)
```{r}
vis.data<-xdata.int%>%
  select(subject, name, trial, condition, frame_count,  x_approx_roll, y_approx_roll, z_approx_roll)%>%
mutate(subject_condition=paste(subject, condition,trial, sep="_"))%>%
  mutate(row = row_number()) %>%
  pivot_wider(names_from=name, values_from=c(x_approx_roll, y_approx_roll, z_approx_roll))%>%
  filter(!is.na(x_approx_roll_head_centre), !is.na(y_approx_roll_head_centre))
##area covered:
##all cells must be of the exact same size, and I feel they should be approximately square
##set approximate edge length of cells in mm:
edge.len=500##this is the one and only thing in the code you can manipulate and are allowed to change
##set limits of the area (certainly, these two need to be adjusted, too; also make sure that there is not a
##a single point falling outside these limits as I don't know what happened in such a case):
xlim=c(0, 7300)
ylim=c(0, 6050)

##source function needed:
source("./functions/area_functions.r")
##determine resolution of the grid in x- and y-direction:
nx=round(diff(xlim)/edge.len)
ny=round(diff(ylim)/edge.len)

xdata.int<-xdata.int%>%mutate(subject_condition=paste(subject, condition,trial, sep="_"))
subjects = unique(xdata.int$subject)
names = unique(xdata.int$name)
conditions =unique(xdata.int$condition)
subject_conditions =unique(xdata.int$subject_condition)

sel = list()
sel2 = list()
ydata = list()
xx = list()
area_covered<-c()
for(subject_condition_ in subject_conditions){

##create vector with the positions used (needed because the first and last position are NA):
ydata[[subject_condition_]]<-vis.data%>%filter(subject_condition==subject_condition_)
sel[[subject_condition_]]=which(apply(!is.na(ydata[[subject_condition_]][, c("x_approx_roll_head_centre", "y_approx_roll_head_centre")]), 1, all))
sel2[[subject_condition_]]=1+which(sel[[subject_condition_]][-1]&sel[[subject_condition_]][-length(sel[[subject_condition_]])])
##determined cells covered:
xx[[subject_condition_]]=lapply(sel2[[subject_condition_]][-1], function(x){
	y=effort.per.cell(grid.left=xlim[1], grid.right=xlim[2], grid.bottom=ylim[1], grid.top=ylim[2], nx=nx, ny=ny, 
		xs=ydata[[subject_condition_]]$x_approx_roll_head_centre[x-1], xe=ydata[[subject_condition_]]$x_approx_roll_head_centre[x], 
		ys=ydata[[subject_condition_]]$y_approx_roll_head_centre[x-1], ye=ydata[[subject_condition_]]$y_approx_roll_head_centre[x])
	apply(y[["effort"]][, c("x.name", "y.name")], 1, paste, collapse="_")
})
##and the area covered is:
area_covered<-c(area_covered, length(unique(unlist(xx[[subject_condition_]])))/(nx*ny))
}

area.data<-as.data.frame(cbind(subject_conditions, area_covered))%>%
  separate(subject_conditions, c("subject", "condition", "trial"))%>%
  mutate(name="head_centre", area_covered=as.numeric(area_covered))

area.data <- area.data %>%
  mutate(trial=as.integer(trial))%>%
  rename(keypoint = name)

area_covered_50cm<-ggplot(data=area.data, aes(x=condition, y=area_covered))+
  geom_boxplot()+
  geom_point()+
  theme_classic()
area_covered_50cm
```

Calculate the tail angle

First the proportion of data available for the tail angle
```{r}
source("./functions/tail_angle_function.r")

frame.count.df<- xdata.int %>%
  ungroup()%>%
  group_by(subject,condition, trial, frame_count)%>%
  summarise(frame_count=mean(frame_count))%>%
  ungroup()

tailtip.data.raw<-xdata.int%>%
  ungroup()%>%
  select(subject, name, condition, trial,  frame_count, x, y)%>%
  filter(name=="tail_tip")%>%
  full_join(frame.count.df)%>%
  mutate(name="tail_tip")

hc.data.raw<-xdata.int%>%
  ungroup()%>%
  select(subject, name, condition, trial,  frame_count, x, y)%>%
  filter(name=="head_centre")%>%
  full_join(frame.count.df)%>%
  mutate(name="head_centre")

tailbase.data.raw<-xdata.int%>%
  ungroup()%>%
  select(subject, name, condition, trial,  frame_count, x, y)%>%
  filter(name=="tail_base")%>%
  full_join(frame.count.df)%>%
  mutate(name="tail_base")



tail.data_raw<-tailtip.data.raw%>%
  full_join(hc.data.raw)%>%
  full_join(tailbase.data.raw)%>%
  mutate(subject_condition=paste(subject, condition,trial, sep="_"))%>%
  group_by(subject, condition, trial, frame_count)%>%
  pivot_wider(names_from=name, values_from=c(x, y))%>%
  unchop(everything())


tail_angles_raw=sapply(1:nrow(tail.data_raw), function(x){
	if(all(!is.na(tail.data_raw[x, c("x_head_centre", "y_head_centre", "x_tail_base", "y_tail_base", "x_tail_tip", "y_tail_tip")]))){

		v.angle(tailtip.loc=c(x=tail.data_raw$x_tail_tip[x],	
		                                        y=tail.data_raw$y_tail_tip[x]),
		                   tailbase.loc=c(x=tail.data_raw$x_tail_base[x],	
		                                        y=tail.data_raw$y_tail_base[x]),
														atlas.loc=c(x=tail.data_raw$x_head_centre[x], 
																				y=tail.data_raw$y_head_centre[x]))
	}else{
		return(NA)
	}
})


tail.angle.data_raw<-as.data.frame(cbind(tail.data_raw, tail_angle=as.numeric(tail_angles_raw)))


```

Then the tail angle.
```{r}
source("./functions/tail_angle_function.r")

tailtip.data<-xdata.int%>%
  ungroup()%>%
  select(subject, name, condition, trial,  frame_count, x_approx_roll, y_approx_roll)%>%
  filter(name=="tail_tip")%>%
  full_join(frame.count.df)%>%
  mutate(name="tail_tip")

hc.data<-xdata.int%>%
  ungroup()%>%
  select(subject, name, condition, trial,  frame_count, x_approx_roll, y_approx_roll)%>%
  filter(name=="head_centre")%>%
  full_join(frame.count.df)%>%
  mutate(name="head_centre")

tailbase.data<-xdata.int%>%
  ungroup()%>%
  select(subject, name, condition, trial,  frame_count, x_approx_roll, y_approx_roll)%>%
  filter(name=="tail_base")%>%
  full_join(frame.count.df)%>%
  mutate(name="tail_base")

tail.data<-tailtip.data%>%
  full_join(hc.data)%>%
  full_join(tailbase.data)%>%
  mutate(subject_condition=paste(subject, condition,trial, sep="_"))%>%
  group_by(subject, condition, trial, frame_count)%>%
  pivot_wider(names_from=name, values_from=c(x_approx_roll, y_approx_roll))%>%
  unchop(everything())


tail_angles=sapply(1:nrow(tail.data), function(x){
	if(all(!is.na(tail.data[x, c("x_approx_roll_head_centre", "y_approx_roll_head_centre", "x_approx_roll_tail_base", "y_approx_roll_tail_base", "x_approx_roll_tail_tip", "y_approx_roll_tail_tip")]))){

		v.angle(tailtip.loc=c(x=tail.data$x_approx_roll_tail_tip[x],	
		                                        y=tail.data$y_approx_roll_tail_tip[x]),
		                   tailbase.loc=c(x=tail.data$x_approx_roll_tail_base[x],	
		                                        y=tail.data$y_approx_roll_tail_base[x]),
														atlas.loc=c(x=tail.data$x_approx_roll_head_centre[x], 
																				y=tail.data$y_approx_roll_head_centre[x]))
	}else{
		return(NA)
	}
})


tail.angle.data<-as.data.frame(cbind(tail.data, tail_angle=as.numeric(tail_angles)))


```

```{r}

tail.angle.ind.data.raw<-tail.angle.data_raw%>%
  group_by(subject, condition, trial)%>%
  summarise(tail_angle_prop_tracked=1-(sum(is.na(tail_angle))/length(tail_angle)))%>%
  ungroup()

tail.angle.ind.data<-tail.angle.data%>%
  group_by(subject, condition, trial)%>%
  summarise(tail_angle_mean=mean(tail_angle, na.rm=TRUE), tail_angle_median=median(tail_angle, na.rm=TRUE))%>%
  ungroup()%>%
  full_join(tail.angle.ind.data.raw)


tail_plot<- ggplot(data=tail.angle.ind.data%>%filter(tail_angle_prop_tracked>0.2), aes(x=reorder(subject, tail_angle_median), y=tail_angle_median))+
  geom_bar(stat="identity")+
  facet_grid(trial~condition)+
 # theme(axis.text.x = element_text(angle = 90,  vjust=0))+
  theme_bw()+
  coord_flip()+
  ylab("Median tail angle")+
  xlab("Subjects")

ggsave(tail_plot, filename = "graphics/tail_plot.png", width = 12, height=12, scale=0.7)
```

Visualise the tail angle:
```{r}
arthur1_teasing_tail_angle<-tail.angle.data%>%filter(subject=="Arthur1", condition=="teasing", trial==4)
juna_blocked4_tail_angle<-tail.angle.data%>%filter(subject=="Juna", condition=="blocked", trial==4)
cappuccina_clumsy3_tail_angle<-tail.angle.data%>%filter(subject=="Cappuccina", condition=="clumsy", trial==3)
```

```{r}
arthur1_teasing_tail_angle_plot<-ggplot(arthur1_teasing_tail_angle, aes(x=x_approx_roll_tail_tip, y=y_approx_roll_tail_tip)) +
    geom_path(col="grey", alpha=0.2) + 
  geom_point(aes(color = tail_angle), alpha=0.15, size = 1) +#
  scale_color_gradient("Tail angle", low = "yellow", high = "darkblue", breaks=c(-90, 0, 90), labels=c("90 (left)", "0", "90 (right)")) + 
       annotate("rect", xmin=object.data$x[object.data$name=="obstacle_l1"], xmax=object.data$x[object.data$name=="obstacle_r1"], ymin=object.data$y[object.data$name=="obstacle_r2"],ymax=object.data$y[object.data$name=="obstacle_r1"], fill="#E8E288", alpha=0.9)+
    annotate("rect", xmin=object.data$x[object.data$name=="chair_l1"], xmax=object.data$x[object.data$name=="chair_r1"], ymin=object.data$y[object.data$name=="chair_r1"],ymax=object.data$y[object.data$name=="chair_r2"], fill="#9BBEC7", alpha=0.9)+
    theme(axis.text.x = element_text(angle = 90)) + 
      ylab("y") + xlab("x") + 
    ylim(0, 6050) + xlim(0, 7300) + 
  theme(plot.title = element_text(size = 24, face = "bold", hjust=0.5), axis.title.x = element_text(size = 16, face = "bold"), axis.title.y = element_text(size = 16, face = "bold"))+
  ggtitle("Tail")



ggsave(arthur1_teasing_tail_angle_plot, filename = "graphics/arthur1_teasing_tail_angle_plot.pdf", width=5.7, height=5, scale=0.8)
```

```{r}
library("viridis") 
cappuccina_clumsy3_tail_angle_plot<-ggplot(cappuccina_clumsy3_tail_angle, aes(x=x_approx_roll_tail_tip, y=y_approx_roll_tail_tip, fill=tail_angle, color=tail_angle)) +
   geom_path(alpha=0.5) + 
  geom_point(alpha=0.15, size = 1.2, pch=19) +#
 # scale_color_gradient("Tail angle", low = "yellow", high = "darkblue", breaks=c(-90, 0, 90), labels=c("90 (left)", "0", "90 (right)")) + 
   scale_fill_viridis(option="viridis", "Tail angle",  breaks=c(-90, 0, 90), labels=c("90 (left)", "0", "90 (right)"))+
  scale_color_viridis(option="viridis", "Tail angle",  breaks=c(-90, 0, 90), labels=c("90 (left)", "0", "90 (right)"))+
       annotate("rect", xmin=object.data$x[object.data$name=="obstacle_l1"], xmax=object.data$x[object.data$name=="obstacle_r1"], ymin=object.data$y[object.data$name=="obstacle_r2"],ymax=object.data$y[object.data$name=="obstacle_r1"], fill="brown", alpha=0.5)+
    annotate("rect", xmin=object.data$x[object.data$name=="chair_l1"], xmax=object.data$x[object.data$name=="chair_r1"], ymin=object.data$y[object.data$name=="chair_r1"],ymax=object.data$y[object.data$name=="chair_r2"], fill="#9BBEC7", alpha=0.9)+
    theme(axis.text.x = element_text(angle = 90)) + 
      ylab("y") + xlab("x") + 
    ylim(0, 6050) + xlim(0, 7300) + 
  theme(plot.title = element_text(size = 24, face = "bold", hjust=0.5), axis.title.x = element_text(size = 16, face = "bold"), axis.title.y = element_text(size = 16, face = "bold"))+
  #ggtitle("Tail")
  theme_bw()

cappuccina_clumsy3_tail_angle_plot

ggsave(cappuccina_clumsy3_tail_angle_plot, filename = "graphics/cappuccina_clumsy3_tail_angle_plot.png", width=11, height=7, scale=0.5)
```

### summary distance data
```{r}
distance.data<-xdata.saved%>%
  group_by(subject, keypoint, condition, trial)%>% 
  summarise(distance.sum=sum(distance, na.rm=TRUE),
            max.frame.count=max(frame_count), min.frame.count=min(frame_count), tracked_data_count=sum(!is.na(x)), prop_tracked_data= tracked_data_count/(max.frame.count+1-min.frame.count), median_err=median(err, na.rm=TRUE),
            mean.distance.chair.owner=mean(distance_chair_owner, na.rm=TRUE), min.distance.chair.owner=min(distance_chair_owner, na.rm=TRUE), prop_chair_owner=sum(duration_chair_owner, na.rm = TRUE)/length(duration_chair_owner))%>%
  ungroup()%>%
  full_join(area.data)%>%
  full_join(tail.angle.ind.data)

write.csv(distance.data, file = "data/unwilling_unable_3D_summary_data.csv")
```


### Proportion of tracked data 
```{r}
#proportion of tracked data by keypoint
prop_tracked_by_keypoint<-distance.data%>%
  group_by(keypoint)%>%
  summarise(mean(prop_tracked_data),median(prop_tracked_data), min(prop_tracked_data),max(prop_tracked_data), mean(median_err, na.rm=TRUE))

write.csv(prop_tracked_by_keypoint, file ="saves/prop_tracked_by_keypoint.csv")

#proportion of tracked data by condition
prop_tracked_by_condition<-distance.data%>%
  group_by(condition)%>%
  summarise(mean(prop_tracked_data), min(prop_tracked_data),max(prop_tracked_data), mean(median_err, na.rm=TRUE))

write.csv(prop_tracked_by_condition, file = "saves/prop_tracked_by_condition.csv")

#data with less than 50% tracked
distance.data%>%
 filter(prop_tracked_data<.5)%>%
  arrange(keypoint)
```

```{r}
save.image("unwilling_unable_3D_workspace.RData")
```

### Heatmap of raw data


```{r}
xdata.int<-xdata.int%>%   mutate(condition=fct_recode(as.factor(condition), "Blocked"="blocked", "Teasing"="teasing", "Clumsy"="clumsy"))%>%
  mutate(condition=fct_relevel(condition, "Blocked", "Teasing","Clumsy"))
```


```{r}
p3<-ggplot(data = xdata.int%>%filter(name=="head_centre"), aes(x=x_approx_roll, y=y_approx_roll))+
  facet_wrap(~condition)+
  theme_bw()+
  #scale_fill_viridis() +
  theme(legend.position = "none")+
       annotate("rect", xmin=object.data$x[object.data$name=="obstacle_l1"], xmax=object.data$x[object.data$name=="obstacle_r1"], ymin=object.data$y[object.data$name=="obstacle_r2"],ymax=object.data$y[object.data$name=="obstacle_r1"], fill="#E8E288", alpha=0.9)+
    annotate("rect", xmin=object.data$x[object.data$name=="chair_l1"], xmax=object.data$x[object.data$name=="chair_r1"], ymin=object.data$y[object.data$name=="chair_r1"],ymax=object.data$y[object.data$name=="chair_r2"], fill="#9BBEC7", alpha=0.9)+
annotate("rect", xmin=chair_window_ia_xl, xmax=chair_window_ia_xr, ymin=chair_window_ia_yl,ymax=6049, fill=NA, color="black", alpha=1)+#caregiver IA
    geom_point(alpha=0.008, color="darkblue", size=0.85)+
    geom_density_2d(color="red")+
    theme_bw()+ 
    ylab("Y coordinates (in m)") + xlab("X coordinates (in m)") + 
    ylim(0, 6050) + xlim(0, 7300) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))
    


#p3



ggsave(p3, filename = "graphics/density_plot.png", width = 15,height=5, scale=0.7 )

```


