---
title: "Unwilling / unable: 3D tracking data processing"
author: "Christoph Voelter"
date: "22/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(summarytools)
library(ggthemes)
library(lubridate)
library(glmmTMB)

source("./functions/diagnostic_fcns.r")
source("./functions/glmm_stability.r")
source("./functions/boot_glmm.r")
source("./functions/glmmTMB_stability.r")
source("./functions/drop1_para_glmmtmb.r")
source("./functions/extract_ranef_gmmTMB.r")

#load("unwilling_unable_3D_analysis.RData")
```

Notes: Pruning of the models in case of convergence issues in the following order:
- remove random slope of control variable trial number
- remove control predictors:  sex, age
- remove random slopes of test predictors

Load data
```{r}
demographics.data<-read.csv(file="data/unwilling_unable_demographics.csv")%>%
  rename(sex=gender)

xdata<-read.csv(file="data/unwilling_unable_3D_summary_data.csv")%>%
  rename(CDL.name=subject)%>%
  select(-X)%>%
  inner_join(demographics.data)
 
view(dfSummary(xdata))
table(xdata$CDL.name, xdata$condition)

```


### Proportion of tracked data 
```{r}
#proportion of tracked data by keypoint
xdata%>%
  group_by(keypoint)%>%
  summarise(mean(prop_tracked_data),median(prop_tracked_data), min(prop_tracked_data),max(prop_tracked_data), mean(median_err))
```

## Area covered

```{r}
library(lme4)
xdata$condition <- as.factor(xdata$condition)
xdata$condition <- relevel(xdata$condition, ref = "blocked")
snout.data<-xdata%>%filter(keypoint=="snout")
hc.data<-xdata%>%filter(keypoint=="head_centre")
tail.data<-xdata%>%filter(keypoint=="tail_tip")

tail.tip.data<-xdata%>%
  filter(CDL.name!="Pebbles3")%>%
  filter(keypoint=="tail_base" | keypoint=="tail_tip")%>%
  select(subjectID, keypoint, distance.sum,  condition, trial, sex, age, block)%>%
  pivot_wider(names_from = keypoint, values_from=distance.sum)%>%
  mutate(tail_tip_diff=tail_tip-tail_base, tail_tip_ratio=tail_tip/tail_base)



hist(hc.data$prop_tracked_data)
hc.data$z.trial<-as.vector(scale(hc.data$trial, center = TRUE, scale=TRUE))
hc.data$z.age<-as.vector(scale(hc.data$age, center = TRUE, scale=TRUE))
hc.data$z.order<-as.vector(scale(hc.data$block, center = TRUE, scale=TRUE))
hc.data$condition.c1=as.vector(scale(as.numeric(hc.data$condition==levels(as.factor(hc.data$condition))[2]), center=TRUE, scale= FALSE))
hc.data$condition.c2=as.vector(scale(as.numeric(hc.data$condition==levels(as.factor(hc.data$condition))[3]), center=TRUE, scale= FALSE))
hc.data$sex<- as.factor(hc.data$sex)

view(dfSummary(hc.data))

hc.data2 <- hc.data
hc.data2$condition <- relevel(hc.data2$condition, ref = "teasing")
hc.data2$condition.c1=as.vector(scale(as.numeric(hc.data2$condition==levels(as.factor(hc.data2$condition))[2]), center=TRUE, scale= FALSE))
hc.data2$condition.c2=as.vector(scale(as.numeric(hc.data2$condition==levels(as.factor(hc.data2$condition))[3]), center=TRUE, scale= FALSE))
```




```{r}
hist(hc.data$area_covered)
min(hc.data$area_covered)
max(hc.data$area_covered)
view(dfSummary(hc.data))
```



```{r}
p1<-ggplot(data=hc.data, aes(x=condition, y=area_covered))+
  geom_jitter()+
  geom_violin(alpha=0.2)
p1
```




```{r}
## code to run the model
hc.data$prop_tracked_data_inv<-1/hc.data$prop_tracked_data
contr<-glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000))

mm1_area=glmmTMB(area_covered~condition+z.trial+z.order+z.age+sex +
            (1|subjectID)+
            (0+condition.c1|subjectID)+(0+condition.c2|subjectID)+
            (0+z.order|subjectID) + (0+z.trial|subjectID),
             weights=prop_tracked_data_inv,
             data=hc.data, family=beta_family, control=contr)

mm1_area_null=glmmTMB(area_covered~z.trial+z.order + z.age+sex +
            (1|subjectID)+
            (0+condition.c1|subjectID)+(0+condition.c2|subjectID)+
            (0+z.order|subjectID) + (0+z.trial|subjectID),
             weights=prop_tracked_data_inv,
             data=hc.data, family=beta_family, control=contr)

anova(mm1_area, mm1_area_null, test="Chisq")

```


```{r}
overdisp.test(mm1_area)

summary(mm1_area)

mm1_area_drop1 <- drop1(mm1_area, test="Chisq")%>% 
  filter(!is.na(Df)) %>% 
  add_row(Df = rep(NA,1),  .before = 1) %>% 
  add_row(Df = rep(NA,1),  .before = 3)
```
relevelling of reference category:
```{r}
hc.data2$prop_tracked_data_inv<-1/hc.data2$prop_tracked_data
mm1_area.rl=glmmTMB(area_covered~condition+z.trial+z.order+ z.age+sex +
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID)+
            (0+z.order|subjectID) + (0+z.trial|subjectID),
             weights=prop_tracked_data_inv,
             data=hc.data2, family=beta_family, control=contr)
summary(mm1_area.rl)
```

```{r}
library(car)
xx=lm(area_covered~condition+z.trial+z.order+ sex+z.age, data=hc.data)
vif(xx)
```
```{r eval=FALSE}
mm1_area_tail.ci=boot.glmmtmb(mm1_area, 
nboots=1000, para=T, n.cores="all-1", resol=1000, level=0.95, data=hc.data)
  
  
```

### output table

```{r}
model_table_area <- bind_cols(as.data.frame(summary(mm1_area)$coefficients$cond),
                              mm1_area_drop1)%>%#,
                            # mm1_area_tail.ci$ci.estimates$fe[1:7,]) %>%
  select(Estimate, SE = `Std. Error`, Chi2 = LRT, df = Df, p = `Pr(>Chi)`, z_wald=`z value`, p_wald=`Pr(>|z|)`) %>% #LowerCI = X2.5., UpperCI = X97.5., 
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
  #mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
mutate(p=replace(p, p==0, "<0.001"))

write.csv(model_table_area, file = "saves/area_mm1_output_table.csv")
```


## Duration in owner proximity

```{r}
hist(hc.data$prop_chair_owner)
min(hc.data$prop_chair_owner)
max(hc.data$prop_chair_owner)
view(dfSummary(hc.data))

hc.data <- hc.data %>%
  mutate(binary_chair_owner=as.numeric(ifelse(prop_chair_owner>0, 1, ifelse(prop_chair_owner==0, 0, NA))))
hist(hc.data$binary_chair_owner)
##code to remove 1 and 0 from the distribution of the response variable
hc.data$prop_chair_owner_scaled <- (hc.data$prop_chair_owner*(length(hc.data$prop_chair_owner) - 1) + 0.5)/length(hc.data$prop_chair_owner)
```

```{r}
p.owner.chair<-ggplot(data=hc.data, aes(x=condition, y=prop_chair_owner))+
  geom_jitter()+
  geom_violin(alpha=0.2)
p.owner.chair
```




```{r}
contr<-glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000))

mm1_duration_owner=glmmTMB(prop_chair_owner_scaled ~ condition+z.trial+z.order+ z.age+sex+
            (1+condition.c1+condition.c2 + z.order + z.trial|subjectID),
             weights=prop_tracked_data_inv,
             data=hc.data, family=beta_family, control=contr)
#convergence issues with beta models --> use binomial model instead
mm1_duration_owner=glmmTMB(prop_chair_owner_scaled ~ condition+z.trial+z.order+ z.age+sex+
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID),
             weights=prop_tracked_data_inv,
             data=hc.data, family=beta_family, control=contr)

```
convergences issues with proportion data --> analyse as binary data
```{r}

library(lme4)

mm1_binary_owner=glmer(binary_chair_owner ~ condition+z.trial+z.order+ z.age+sex+
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID) + (0+z.order|subjectID)+ 
            (0+z.trial|subjectID),
             data=hc.data, family=binomial, 
            control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(mm1_binary_owner)
```
```{r}
hc.data2 <- hc.data2 %>%
  mutate(binary_chair_owner=as.numeric(ifelse(prop_chair_owner>0, 1, ifelse(prop_chair_owner==0, 0, NA))))
hist(hc.data2$binary_chair_owner)

mm1_binary_owner_rl=glmer(binary_chair_owner ~ condition+z.trial+z.order+ z.age+ sex+
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID) + (0+z.order|subjectID)+ 
            (0+z.trial|subjectID),
             data=hc.data2, family=binomial, 
            control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(mm1_binary_owner_rl)
```

```{r}

mm1_binary_owner_drop1 <- drop1(mm1_binary_owner, test="Chisq")%>% 
  filter(!is.na(npar)) %>% 
  add_row(npar = rep(NA,1),  .before = 1) %>% 
  add_row(npar = rep(NA,1),  .before = 3)
```


```{r}
library(car)
xx=lm(binary_chair_owner ~ condition+z.trial+z.order+ sex+z.age, data=hc.data)
vif(xx)
```

```{r}
mm1_binary_owner.ci=boot.lmer(mm1_binary_owner, discard.warnings=F,
nboots=1000, para=T, n.cores="all-1", resol=1000, level=0.95)
  
  #boot.glmmtmb(mm2,tail.tip.data, nboots=1000, para=T, n.cores = "all-1", )

```


### output table


```{r}
model_owner_IA <- bind_cols(as.data.frame(summary(mm1_binary_owner)$coeff),
                              mm1_binary_owner_drop1,
                             mm1_binary_owner.ci$ci.estimates) %>%
  select(Estimate, SE = `Std. Error`,LowerCI = X2.5., UpperCI = X97.5., Chi2 = LRT, df = npar, p = `Pr(Chi)`, z_wald=`z value`, p_wald=`Pr(>|z|)`) %>% # 
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
  #mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
mutate(p=replace(p, p==0, "<0.001"))

write.csv(model_owner_IA, file = "saves/mm1_binary_owner_output_table.csv")
```


## Tail angle
positive values: right side, negative values left side

```{r}

tail.data <- tail.data %>%
  filter(CDL.name!="Pebbles3")%>% #dog with a docked tail
  full_join(tail.tip.data)

tail.data$z.trial<-as.vector(scale(tail.data$trial, center = TRUE, scale=TRUE))
tail.data$z.age<-as.vector(scale(tail.data$age, center = TRUE, scale=TRUE))
tail.data$z.order<-as.vector(scale(tail.data$block, center = TRUE, scale=TRUE))
tail.data$condition.c1=as.vector(scale(as.numeric(tail.data$condition==levels(as.factor(tail.data$condition))[2]), center=TRUE, scale= FALSE))
tail.data$condition.c2=as.vector(scale(as.numeric(tail.data$condition==levels(as.factor(tail.data$condition))[3]), center=TRUE, scale= FALSE))
tail.data$sex<- as.factor(tail.data$sex)

view(dfSummary(tail.data))

hist(tail.data$tail_angle_mean)
hist(tail.data$tail_angle_prop_tracked)

tail.data$tail_angle_mean_pos <- (tail.data$tail_angle_mean + 180) 
tail.data$tail_angle_mean_prop <- tail.data$tail_angle_mean_pos  / 360 
trans<-powerTransform(tail.data$tail_angle_mean_pos)$lambda
tail.data$log_tail_angle_mean_pos<-((tail.data$tail_angle_mean_pos^trans-1)/trans)
hist(tail.data$log_tail_angle_mean_pos)
max(tail.data$tail_angle_mean_prop)
```

```{r}
library(lme4)

mm1.tail.angle.beta=glmmTMB(tail_angle_mean_prop~condition + z.trial+z.order +  z.age + sex +
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID) + (0+z.order|subjectID)+ 
            (0+z.trial|subjectID),
            , data=tail.data, family=beta_family, control=contr)


mm1.tail.angle<-lme4::lmer(tail_angle_mean~condition + z.trial+z.order +  z.age + sex +
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID) + (0+z.order|subjectID)+ 
            (0+z.trial|subjectID), data=tail.data, REML=FALSE)

mm1.tail.angle.null<-lme4::lmer(tail_angle_mean~z.trial+z.order +  z.age + sex +
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID) + (0+z.order|subjectID)+ 
            (0+z.trial|subjectID), data=tail.data, REML=FALSE)

anova(mm1.tail.angle, mm1.tail.angle.null,  test = "Chisq")
summary(mm1.tail.angle)
```


```{r}
diagnostics.plot(mm1.tail.angle, size.fac=2)

ranef.diagn.plot(mm1.tail.angle)
```

```{r}
drop1_mm1.tail.angle <- drop1(mm1.tail.angle, test="Chisq")%>%filter(!is.na(npar))%>%add_row(npar = rep(NA,1),  .before = 1)%>%add_row(npar = rep(NA,1),  .before = 3)
drop1_mm1.tail.angle

drop1(mm1.tail.angle.beta, test="Chisq") #results of beta model confirm LMM 
```
Individual fixed effects
```{r}
library(lmerTest)
mm1.tail.angle.reml<-lmer(tail_angle_mean~condition + z.trial+z.order + z.age + sex +
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID) + (0+z.order|subjectID)+ 
            (0+z.trial|subjectID), data=tail.data, REML=TRUE)
summary(mm1.tail.angle.reml)
```

```{r}
tail.data2 <- tail.data
tail.data2$condition <- relevel(tail.data2$condition, ref = "teasing")
tail.data2$condition.c1=as.vector(scale(as.numeric(tail.data2$condition==levels(as.factor(tail.data2$condition))[2]), center=TRUE, scale= FALSE))
tail.data2$condition.c2=as.vector(scale(as.numeric(tail.data2$condition==levels(as.factor(tail.data2$condition))[3]), center=TRUE, scale= FALSE))


mm1.tail.angle.reml.rl<-lmer(tail_angle_mean~condition + z.trial+z.order + z.age + sex +
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID) + (0+z.order|subjectID)+ 
            (0+z.trial|subjectID),  data=tail.data2, REML=TRUE)
summary(mm1.tail.angle.reml.rl)
```


```{r}
library(car)
xx=lm(tail_angle_mean~condition + z.trial+z.order + sex + z.age, data=hc.data)
vif(xx)
```
relative model complexity
```{r}
length(residuals(mm1.tail.angle))/
(length(fixef(mm1.tail.angle))+
nrow(as.data.frame(summary(mm1.tail.angle)$varcor)))
```
model stability
```{r}

mm1.tail.angle.stab=glmm.model.stab(model.res=mm1.tail.angle, contr=NULL, para=F, data=NULL)

mm1.tail.angle.stab$summary

m.stab.plot(round(mm1.tail.angle.stab$summary[, -1], 3))
```
--> model stable with regard to the fixed effects

```{r}
boot.mm1.tail.angle=boot.lmer(mm1.tail.angle, discard.warnings=F,
nboots=1000, para=T, n.cores="all-1", resol=1000, level=0.95)

mm1.tail.angle_boot_ci<-boot.mm1.tail.angle$ci.estimates
```
### effect size
```{r}
library(MuMIn)
r.squaredGLMM(mm1.tail.angle)
```


### output table

```{r}


model_table_mm1.tail.angle <- bind_cols(as.data.frame(summary(mm1.tail.angle)$coefficients),
                         drop1_mm1.tail.angle,
                         mm1.tail.angle_boot_ci) %>% #mm2_boot_ci<-boot.full$ci.estimates
  select(Estimate, SE = `Std. Error`, LowerCI = X2.5., UpperCI = X97.5., Chi2 = LRT, df = npar, p = `Pr(Chi)`) %>%
  mutate(across(.cols = c(p), ~ round(.x, 3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ round(.x, 2))) %>% 
  #mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
mutate(p=replace(p, p==0, "<0.001"))

write.csv(model_table_mm1.tail.angle , file = "saves/tail_angle_mm1_output_table.csv")
```

## Tail angle: Weighting by tail movements
```{r}

mm1.tail.angle.beta_tail_ratio=glmmTMB(tail_angle_mean_prop~condition + z.trial+z.order +  z.age + sex +
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID) + (0+z.order|subjectID)+ 
            (0+z.trial|subjectID),
            weights=tail_tip_ratio, data=tail.data, family=beta_family, control=contr)

summary(mm1.tail.angle.beta_tail_ratio)

mm1.tail.angle_tail_ratio<-lme4::lmer(tail_angle_mean~condition + z.trial+z.order +  z.age + sex +
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID) + (0+z.order|subjectID)+ 
            (0+z.trial|subjectID), weights=tail_tip_ratio, data=tail.data, REML=FALSE)

mm1.tail.angle.null_tail_ratio<-lme4::lmer(tail_angle_mean~z.trial+z.order +  z.age + sex +
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID) + (0+z.order|subjectID)+ 
            (0+z.trial|subjectID), weights=tail_tip_ratio, data=tail.data, REML=FALSE)

anova(mm1.tail.angle_tail_ratio, mm1.tail.angle.null_tail_ratio,  test = "Chisq")
summary(mm1.tail.angle)
```



```{r}
diagnostics.plot(mm1.tail.angle_tail_ratio, size.fac=2)

ranef.diagn.plot(mm1.tail.angle_tail_ratio)
```

```{r}
drop1_mm1.tail.angle_tail_ratio <- drop1(mm1.tail.angle_tail_ratio, test="Chisq")%>%filter(!is.na(npar))%>%add_row(npar = rep(NA,1),  .before = 1)%>%add_row(npar = rep(NA,1),  .before = 3)
drop1_mm1.tail.angle_tail_ratio

drop1(mm1.tail.angle.beta_tail_ratio, test="Chisq") #results of beta model confirm LMM 
```
Individual fixed effects
```{r}
library(lmerTest)
mm1.tail.angle.reml_tail_ratio<-lmer(tail_angle_mean~condition + z.trial+z.order + z.age + sex +
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID) + (0+z.order|subjectID)+ 
            (0+z.trial|subjectID), weights=tail_tip_ratio, data=tail.data, REML=TRUE)
summary(mm1.tail.angle.reml_tail_ratio)
```

```{r}
tail.data2 <- tail.data
tail.data2$condition <- relevel(tail.data2$condition, ref = "teasing")
tail.data2$condition.c1=as.vector(scale(as.numeric(tail.data2$condition==levels(as.factor(tail.data2$condition))[2]), center=TRUE, scale= FALSE))
tail.data2$condition.c2=as.vector(scale(as.numeric(tail.data2$condition==levels(as.factor(tail.data2$condition))[3]), center=TRUE, scale= FALSE))


mm1.tail.angle.reml.rl_tail_ratio<-lmer(tail_angle_mean~condition + z.trial+z.order + z.age + sex +
            (1|subjectID)+
            (0+condition.c1+condition.c2|subjectID) + (0+z.order|subjectID)+ 
            (0+z.trial|subjectID), weights=tail_tip_ratio, data=tail.data2, REML=TRUE)
summary(mm1.tail.angle.reml.rl_tail_ratio)
```


```{r}
boot.mm1.tail.angle_tail_ratio=boot.lmer(mm1.tail.angle_tail_ratio, discard.warnings=F,
nboots=1000, para=T, n.cores="all-1", resol=1000, level=0.95)

mm1.tail.angle_boot_ci_tail_ratio<-boot.mm1.tail.angle_tail_ratio$ci.estimates
```
### effect size
```{r}
library(MuMIn)
r.squaredGLMM(mm1.tail.angle_tail_ratio)
```


### output table

```{r}


model_table_mm1.tail.angle_tail_ratio <- bind_cols(as.data.frame(summary(mm1.tail.angle_tail_ratio)$coefficients),
                         drop1_mm1.tail.angle_tail_ratio,
                         mm1.tail.angle_boot_ci_tail_ratio) %>% #mm2_boot_ci<-boot.full$ci.estimates
  select(Estimate, SE = `Std. Error`, LowerCI = X2.5., UpperCI = X97.5., Chi2 = LRT, df = npar, p = `Pr(Chi)`) %>%
  mutate(across(.cols = c(p), ~ round(.x, 3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ round(.x, 2))) %>% 
  #mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
mutate(p=replace(p, p==0, "<0.001"))

write.csv(model_table_mm1.tail.angle_tail_ratio , file = "saves/tail_angle_weighted_on_tail_ratio_mm1_output_table.csv")
```



```{r}
hc.data.agg <- hc.data %>%
  group_by(condition, subjectID) %>%
  summarise(mean.angle = mean(tail_angle_mean))

ggplot(data=hc.data.agg, aes(x=mean.angle)) +
      geom_histogram(alpha=0.8) + 
  coord_polar(theta="x", start=pi)+
  facet_wrap(~condition)

ggplot(data=hc.data.agg, aes(x=mean.angle)) +
      geom_histogram(alpha=0.8) + 
  facet_wrap(~condition)

ggplot(data=hc.data.agg, aes(x=condition, y=mean.angle)) +
      geom_boxplot(alpha=0.8)+
  geom_jitter()
```



## Plotting

```{r}
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
       
raincloud_theme = theme(
text = element_text(size = 10),
axis.title.x = element_text(size = 16),
axis.title.y = element_text(size = 16),
axis.text = element_text(size = 14),
axis.text.x = element_text(angle = 45, vjust = 0.5),
legend.title=element_text(size=16),
legend.text=element_text(size=16),
legend.position = "right",
plot.title = element_text(lineheight=.8, face="bold", size = 16),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))
```

#### Area covered plot
```{r}

plot.data<-hc.data%>%
  mutate(condition=fct_relevel(condition, "blocked", "teasing","clumsy")) %>%
  group_by(subjectID, condition)%>%
  summarise(mean_area = mean(area_covered), mean_owner_IA = mean(binary_chair_owner), mean_tail_angle = mean(tail_angle_mean))

levels(plot.data$condition2)
plot.data$condition2 <- jitter(as.numeric(as.factor(plot.data$condition), amount = .0001))

library(gghalves)
max(plot.data$mean_area)

area_plot <- ggplot(data = plot.data, aes(x = condition, y= mean_area)) +
      geom_line(aes(x = condition2, group = subjectID), color = "darkgray", lty = 1, alpha = .3) +
  geom_point(data = plot.data %>% filter(condition == "blocked"), aes(x = condition2), color = "dodgerblue", size = 1.5, alpha = .5) +
  geom_point(data = plot.data %>% filter(condition == "clumsy"), aes(x = condition2), color = "darkorange", size = 1.5, alpha = .5, ) +
    geom_point(data = plot.data %>% filter(condition == "teasing"), aes(x = condition2), color = "darkgreen", size = 1.5, alpha = .5, ) +
     geom_half_boxplot(
     data = plot.data %>% filter(condition == "blocked"), aes(x = condition2, y = mean_area), position = position_nudge(x = 2.3), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'dodgerblue', alpha = .5) +
   
   geom_half_boxplot(
     data = plot.data %>% filter(condition == "clumsy"), aes(x = condition2, y = mean_area), position = position_nudge(x = 0.8), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkorange', alpha = .5) +
  
     geom_half_boxplot(
     data = plot.data %>% filter(condition == "teasing"), aes(x = condition2, y = mean_area), position = position_nudge(x = 1.55), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkgreen', alpha = .5) +
    # Define additional settings
  xlab("Condition") +
  ylab("Proportion area visited") +
  scale_x_continuous(breaks = c(1, 2, 3), labels = c("Blocked", "Teasing", "Clumsy"), limits = c(0.75,4)) +
  ylim(0, 0.25) +
  theme_classic()

area_plot

ggsave(area_plot , filename = "graphics/unwilling_unable_area_plot.png", width = 8, height = 8, scale = 0.4)

```



#### Caregiver IA
```{r}

library(gghalves)
max(plot.data$mean_area)

caregiverIA_plot <- ggplot(data = plot.data, aes(x = condition, y= mean_owner_IA)) +
      geom_line(aes(x = condition2, group = subjectID), color = "darkgray", lty = 1, alpha = .3) +
  geom_point(data = plot.data %>% filter(condition == "blocked"), aes(x = condition2), color = "dodgerblue", size = 1.5, alpha = .5) +
  geom_point(data = plot.data %>% filter(condition == "clumsy"), aes(x = condition2), color = "darkorange", size = 1.5, alpha = .5, ) +
    geom_point(data = plot.data %>% filter(condition == "teasing"), aes(x = condition2), color = "darkgreen", size = 1.5, alpha = .5, ) +
     geom_half_boxplot(
     data = plot.data %>% filter(condition == "blocked"), aes(x = condition2, y = mean_owner_IA), position = position_nudge(x = 2.3), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'dodgerblue', alpha = .5) +
   
   geom_half_boxplot(
     data = plot.data %>% filter(condition == "clumsy"), aes(x = condition2, y = mean_owner_IA), position = position_nudge(x = 0.8), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkorange', alpha = .5) +
  
     geom_half_boxplot(
     data = plot.data %>% filter(condition == "teasing"), aes(x = condition2, y = mean_owner_IA), position = position_nudge(x = 1.55), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkgreen', alpha = .5) +
    # Define additional settings
  xlab("Condition") +
  ylab("Caregiver IA visited") +
  scale_x_continuous(breaks = c(1, 2, 3), labels = c("Blocked", "Teasing", "Clumsy"), limits = c(0.75,4)) +
  ylim(0, 1) +
  theme_classic()

caregiverIA_plot

ggsave(caregiverIA_plot , filename = "graphics/unwilling_unable_caregiverIA_plot.png", width = 8, height = 8, scale = 0.4)

```



#### Tail angle plot
```{r}


tailangle_plot <- ggplot(data = plot.data, aes(x = condition, y= mean_tail_angle)) +
  geom_hline(yintercept = 0, lty=2, col="darkgrey")+
      geom_line(aes(x = condition2, group = subjectID), color = "darkgray", lty = 1, alpha = .3) +
  geom_point(data = plot.data %>% filter(condition == "blocked"), aes(x = condition2), color = "dodgerblue", size = 1.5, alpha = .5) +
  geom_point(data = plot.data %>% filter(condition == "clumsy"), aes(x = condition2), color = "darkorange", size = 1.5, alpha = .5, ) +
    geom_point(data = plot.data %>% filter(condition == "teasing"), aes(x = condition2), color = "darkgreen", size = 1.5, alpha = .5, ) +
     geom_half_boxplot(
     data = plot.data %>% filter(condition == "blocked"), aes(x = condition2, y = mean_tail_angle), position = position_nudge(x = 2.3), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'dodgerblue', alpha = .5) +
   
   geom_half_boxplot(
     data = plot.data %>% filter(condition == "clumsy"), aes(x = condition2, y = mean_tail_angle), position = position_nudge(x = 0.8), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkorange', alpha = .5) +
  
     geom_half_boxplot(
     data = plot.data %>% filter(condition == "teasing"), aes(x = condition2, y = mean_tail_angle), position = position_nudge(x = 1.55), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkgreen', alpha = .5) +
    # Define additional settings
  xlab("Condition") +
  ylab("Mean tail angle (in deg)") +
  scale_x_continuous(breaks = c(1, 2, 3), labels = c("Blocked", "Teasing", "Clumsy"), limits = c(0.75,4)) +
  ylim(-180, 180) +
  theme_classic()

tailangle_plot

ggsave(tailangle_plot , filename = "graphics/unwilling_unable_tailangle_plot.png", width = 8, height = 8, scale = 0.4)

```





```{r}
library(cowplot)
pg1<-plot_grid(area_plot, caregiverIA_plot, tailangle_plot, ncol=3,  labels=c("B", "C", "D"))

ggsave(pg1, filename = "graphics/dog_unwillig-unable_pg3.png", width=18, height=6, scale=0.6)
```

```{r}

library(cowplot)
pg2<-plot_grid(p3, pg1 , nrow=2,  labels=c("A", ""))

ggsave(pg2, filename = "graphics/unwilling_unable_pg2.png", width=18, height=12, scale=0.6)
```

```{r}
save.image("unwilling_unable_3D_analysis.RData")
```
