---
title: "Unwilling-unable analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lme4)
library(summarytools)
library(glmmTMB)
library(car)

source("./functions/diagnostic_fcns.r")
source("./functions/glmm_stability.r")
source("./functions/boot_glmm.r")
source("./functions/glmmTMB_stability.r")
source("./functions/drop1_para_glmmtmb.r")

load("unwilling_unable_analysis.RData")

```

load demographics
```{r}
demo.data <- read.csv(file = "data/unwilling_unable_demographics.csv") %>%
  select(-comments.dogs)%>%
  rename(subject=CDL.name)

view(dfSummary(demo.data))

demo.data %>% 
  filter(condition=="blocked")%>%
  summarise(mean(age), min(age), max(age), sum(gender=="F"), sum(gender=="M"))
```
Load data
```{r}
xdata <- read.csv(file = "data/unwilling_unable_scoring_data.csv")

view(dfSummary(xdata))
table(xdata$subject, xdata$trial)
table(xdata$subject, xdata$condition)

```

aggregating data per trial

```{r}
agg.data<-xdata %>%
  mutate(Value=fct_recode(as.factor(Value), "rest"="sitting_down", "rest"="laying_down"))%>%
  mutate(look_away=ifelse(Value=="look_away", 1, NA), pawing=ifelse(Value=="pawing", 1, NA))%>%
  group_by(subject, condition, trial, Behaviour, Value)%>%
  summarise(sum_duration=sum(duration), look_away=sum(look_away), pawing=sum(pawing))%>%
  ungroup()%>%
  droplevels()%>%
  complete(subject, condition, trial, Value, fill=list(sum.duration=0))%>% #fill in 0s
  complete(subject, condition, trial, Value, fill=list(look_away=0))%>%
  complete(subject, condition, trial, Value, fill=list(pawing=0))%>%
  inner_join(demo.data)%>%
  rename(sex=gender)%>%
  replace_na(list(sum_duration=0))
view(dfSummary(agg.data))
```


do trial durations vary across conditions?
```{r}
trial.duration<-agg.data%>%
  filter(Behaviour=="trial")%>%
  rename(trial_duration=sum_duration)%>%
  select(-Behaviour, -Value)

hist(trial.duration$trial_duration)

trial.duration%>%
  group_by(condition)%>%
  summarise(mean=mean(trial_duration), median=median(trial_duration), min=min(trial_duration), max=max(trial_duration))


ggplot(data=trial.duration, aes(x=condition, y=trial_duration))+
  geom_boxplot()+
  geom_point()

```


```{r}

prop.data<-agg.data%>%
   filter(Value!="1", Value!="2", Value!="3", Value!="4")%>%
  full_join(trial.duration)%>%
  mutate(prop.duration=sum_duration/trial_duration)

ggplot(data=prop.data, aes(x=condition, y=prop.duration))+
  geom_boxplot(alpha=0.6)+
  geom_point(alpha=0.1)+
  
  facet_wrap(~Value)

```


## Walk away response

```{r}
model.data.away<-prop.data%>%
    filter(Value=="walk_away")

model.data.away$z.trial<-scale(model.data.away$trial, center = TRUE, scale=TRUE)
model.data.away$z.order<-scale(model.data.away$block, center = TRUE, scale=TRUE)
model.data.away$z.age<-scale(model.data.away$age, center = TRUE, scale=TRUE)
model.data.away$condition<- as.factor(model.data.away$condition)
model.data.away$condition.c1=as.vector(scale(as.numeric(model.data.away$condition==levels(as.factor(model.data.away$condition))[2]), center=TRUE, scale= FALSE))
model.data.away$condition.c2=as.vector(scale(as.numeric(model.data.away$condition==levels(as.factor(model.data.away$condition))[3]), center=TRUE, scale= FALSE))


model.data.away$prop.duration.scaled <- (model.data.away$prop.duration*(length(model.data.away$prop.duration) - 1) + 0.5)/length(model.data.away$prop.duration)#transform DV to exclude 0 and 1s
```


```{r}
library(glmmTMB)
m1.away<-glmmTMB(prop.duration.scaled ~ condition + z.trial + z.order + z.age + sex+(1+(condition.c1+condition.c2)+z.trial+z.order|subject), family=beta_family, data=model.data.away,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))
#convergence issues

#fit the model without the correlations between random intercept and random slopes
m1.away<-glmmTMB(prop.duration.scaled ~ condition + z.trial + z.order + z.age + sex+(1|subject)+(0+condition.c1|subject)+(0+condition.c2|subject)+(0+z.trial|subject)+(0+z.order|subject), family=beta_family, data=model.data.away,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

overdisp.test(m1.away)

```
```{r}
drop1_m1<-drop1(m1.away, test="Chisq")%>%add_row(Df = rep(NA,1),  .before = 3)
```

```{r}
summary(m1.away)
```


```{r}
model.data.away$condition.relevelled<-relevel(model.data.away$condition, ref = "teasing")
levels(model.data.away$condition.relevelled)
model.data.away$condition.rl.c1=as.vector(scale(as.numeric(model.data.away$condition.relevelled==levels(as.factor(model.data.away$condition.relevelled))[2]), center=TRUE, scale= FALSE))
model.data.away$condition.rl.c2=as.vector(scale(as.numeric(model.data.away$condition.relevelled==levels(as.factor(model.data.away$condition.relevelled))[3]), center=TRUE, scale= FALSE))

m1.away.relevelled<-glmmTMB(prop.duration.scaled ~ condition.relevelled + z.trial + z.order + z.age + sex+(1|subject)+(0+condition.rl.c1|subject)+(0+condition.rl.c2|subject)+(0+z.trial|subject)+(0+z.order|subject), family=beta_family, data=model.data.away,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

summary(m1.away.relevelled)
```







model stability
```{r}

m1.stab=glmmTMB.stab(model.res=m1.away, para=F, data=model.data.away)

m1.stab$summary

m.stab.plot(round(m1.stab$summary[, -1], 3))
```



```{r}
library(car)
xx=lm(prop.duration.scaled ~ condition + z.trial + z.order + z.age + sex, data=model.data.away)
vif(xx)
```


```{r}
boot.m1.away<-boot.glmmTMB(m1.away, data=model.data.away,
nboots=1000, para=T, n.cores=3, resol=100, level=0.95)


```



### output table

```{r}

model_table_away<- bind_cols(as.data.frame(summary(m1.away)$coefficients$cond),
                             boot.m1.away$ci.estimates$fe[1:7,],
                             drop1_m1) %>%
                             select(Estimate, SE = `Std. Error`,LowerCI = X2.5., UpperCI = X97.5., z=`z value`, p=`Pr(>|z|)`,  Chi2 = LRT, df = Df, p_LRT = `Pr(>Chi)`) %>%
  mutate(across(.cols = c(p, p_LRT), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:z, Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
#  mutate(across(Chi2:p_LRT, ~replace_na(.x, "")))%>%
mutate(p_LRT=replace(p_LRT, p_LRT==0.000, "<0.001"))%>%
mutate(p=replace(p, p==0.000, "<0.001"))

write.csv(model_table_away, file = "saves/m1_results_prop_away.csv")
```


### Sitting / lying down analysis

```{r}
model.data.rest<-prop.data%>%
    filter(Value=="rest")

model.data.rest$z.trial<-scale(model.data.rest$trial, center = TRUE, scale=TRUE)
model.data.rest$z.order<-scale(model.data.rest$block, center = TRUE, scale=TRUE)
model.data.rest$z.age<-scale(model.data.rest$age, center = TRUE, scale=TRUE)
model.data.rest$condition<- as.factor(model.data.rest$condition)
model.data.rest$condition.c1=as.vector(scale(as.numeric(model.data.rest$condition==levels(as.factor(model.data.rest$condition))[2]), center=TRUE, scale= FALSE))
model.data.rest$condition.c2=as.vector(scale(as.numeric(model.data.rest$condition==levels(as.factor(model.data.rest$condition))[3]), center=TRUE, scale= FALSE))
model.data.rest$sex<- as.factor(model.data.rest$sex)


model.data.rest$prop.duration.scaled <- (model.data.rest$prop.duration*(length(model.data.rest$prop.duration) - 1) + 0.5)/length(model.data.rest$prop.duration)#transform DV to exclude 0 and 1s


m1.rest<-glmmTMB(prop.duration.scaled ~ condition + z.trial + z.order + z.age + sex+(1+condition.c1+condition.c2+z.trial+z.order|subject), family=beta_family, data=model.data.rest,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))
#convergence issues

#fit the model without the correlations between random intercept and random slopes
m1.rest<-glmmTMB(prop.duration.scaled ~ condition + z.trial + z.order + z.age + sex+(1|subject)+(0+condition.c1|subject)+(0+condition.c2|subject)+(0+z.trial|subject)+(0+z.order|subject), family=beta_family, data=model.data.rest,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

overdisp.test(m1.rest)

```
model stability
```{r}

m1.rest.stab=glmmTMB.stab(model.res=m1.rest, para=F, data=model.data.rest)

m1.rest.stab$summary

m.stab.plot(round(m1.rest.stab$summary[, -1], 3))
```

```{r}
drop1_m1.rest<-drop1(m1.rest, test="Chisq")%>%add_row(Df = rep(NA,1),  .before = 3)
```

```{r}
summary(m1.rest)
```

```{r}
model.data.rest$condition.relevelled<-relevel(model.data.rest$condition, ref = "teasing")
levels(model.data.rest$condition.relevelled)
model.data.rest$condition.rl.c1=as.vector(scale(as.numeric(model.data.rest$condition.relevelled==levels(as.factor(model.data.rest$condition.relevelled))[2]), center=TRUE, scale= FALSE))
model.data.rest$condition.rl.c2=as.vector(scale(as.numeric(model.data.rest$condition.relevelled==levels(as.factor(model.data.rest$condition.relevelled))[3]), center=TRUE, scale= FALSE))


m1.away.relevelled<-glmmTMB(prop.duration.scaled ~ condition.relevelled + z.trial + z.order + z.age + sex+(1|subject)+(0+model.data.rest$condition.rl.c1|subject)+(0+model.data.rest$condition.rl.c2|subject)+(0+z.trial|subject)+(0+z.order|subject), family=beta_family, data=model.data.rest,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

summary(m1.away.relevelled)
```

```{r}
library(car)
xx=lm(prop.duration.scaled ~ condition + z.trial + z.order + z.age + sex, data=model.data.rest)
vif(xx)
```


```{r}
boot.m1.rest<-boot.glmmTMB(m1.rest, data=model.data.rest,
nboots=1000, para=T, n.cores=3, resol=100, level=0.95)
```



### output table

```{r}

model_table_rest<- bind_cols(as.data.frame(summary(m1.rest)$coefficients$cond),
                             boot.m1.rest$ci.estimates$fe[1:7,],
                             drop1_m1.rest) %>%
                             select(Estimate, SE = `Std. Error`,LowerCI = X2.5., UpperCI = X97.5., z=`z value`, p=`Pr(>|z|)`,  Chi2 = LRT, df = Df, p_LRT = `Pr(>Chi)`) %>%
  mutate(across(.cols = c(p, p_LRT), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:z, Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
#  mutate(across(Chi2:p_LRT, ~replace_na(.x, "")))%>%
mutate(p_LRT=replace(p_LRT, p_LRT==0.000, "<0.001"))%>%
mutate(p=replace(p, p==0.000, "<0.001"))

write.csv(model_table_rest, file = "saves/m1_results_prop_rest.csv")
```


### Look away analysis

```{r}
model.data.look<-agg.data%>%
    filter(Value=="look_away")%>%
    mutate(look_away_binary=ifelse(look_away>0,1,ifelse(look_away==0, 0, NA)))

model.data.look$z.trial<-scale(model.data.look$trial, center = TRUE, scale=TRUE)
model.data.look$z.order<-scale(model.data.look$block, center = TRUE, scale=TRUE)
model.data.look$z.age<-scale(model.data.look$age, center = TRUE, scale=TRUE)
model.data.look$condition<- as.factor(model.data.look$condition)
model.data.look$condition.c1=as.vector(scale(as.numeric(model.data.look$condition==levels(as.factor(model.data.look$condition))[2]), center=TRUE, scale= FALSE))
model.data.look$condition.c2=as.vector(scale(as.numeric(model.data.look$condition==levels(as.factor(model.data.look$condition))[3]), center=TRUE, scale= FALSE))
model.data.look$sex<- as.factor(model.data.look$sex)

contr <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000000))

m1.look<-glmer(look_away_binary ~ condition + z.trial + z.order + z.age + sex+(1+(condition.c1+condition.c2)+z.trial+z.order|subject), family=binomial, data=model.data.look, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000000)))
```
model stability
```{r}

m1.look.stab=glmm.model.stab(model.res=m1.look, para=F, data=model.data.look)

m1.look.stab$summary

m.stab.plot(round(m1.look.stab$summary[, -1], 3))
```

```{r}
drop1_m1.look<-drop1(m1.look, test="Chisq", control=contr)

drop1_m1.look2<-drop1_m1.look%>%add_row(npar = rep(NA,1), .before = 3)
```

```{r}
summary(m1.look)
```

```{r}
model.data.look$condition.relevelled<-relevel(model.data.look$condition, ref = "teasing")
levels(model.data.look$condition.relevelled)
model.data.look$condition.rl.c1=as.vector(scale(as.numeric(model.data.look$condition.relevelled==levels(as.factor(model.data.look$condition.relevelled))[2]), center=TRUE, scale= FALSE))
model.data.look$condition.rl.c2=as.vector(scale(as.numeric(model.data.look$condition.relevelled==levels(as.factor(model.data.look$condition.relevelled))[3]), center=TRUE, scale= FALSE))

contr <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000000))

m1.look.rel<-glmer(look_away_binary ~ condition.relevelled + z.trial + z.order + z.age + sex+(1+(condition.rl.c1+condition.rl.c2)+z.trial+z.order|subject), family=binomial, data=model.data.look, control = contr)

summary(m1.look.rel)
```

```{r}
library(car)
xx=lm(look_away_binary ~ condition + z.trial + z.order + z.age + sex, data=model.data.look)
vif(xx)
```


```{r}
boot.m1.look<-boot.glmm.pred(m1.look, nboots=1000, para=T, n.cores=3, resol=100, level=0.95)


```



### output table

```{r}

model_table_look<- bind_cols(as.data.frame(summary(m1.look)$coefficients),
                             boot.m1.look$ci.estimates,
                             drop1_m1.look2) %>%
                             select(Estimate, SE = `Std. Error`,LowerCI = X2.5., UpperCI = X97.5., z=`z value`, p=`Pr(>|z|)`,  Chi2 = LRT, df = npar, p_LRT = `Pr(Chi)`) %>%
  mutate(across(.cols = c(p, p_LRT), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:z, Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
#  mutate(across(Chi2:p_LRT, ~replace_na(.x, "")))%>%
mutate(p_LRT=replace(p_LRT, p_LRT==0.000, "<0.001"))%>%
mutate(p=replace(p, p==0.000, "<0.001"))

write.csv(model_table_look, file = "saves/m1_results_look.csv")
```



### Lateral approach


```{r}
model.data.lateral_approach<-prop.data%>%
    filter(Value=="lateral_approach")

model.data.lateral_approach$z.trial<-scale(model.data.lateral_approach$trial, center = TRUE, scale=TRUE)
model.data.lateral_approach$z.order<-scale(model.data.lateral_approach$block, center = TRUE, scale=TRUE)
model.data.lateral_approach$z.age<-scale(model.data.lateral_approach$age, center = TRUE, scale=TRUE)
model.data.lateral_approach$condition<- as.factor(model.data.lateral_approach$condition)
model.data.lateral_approach$condition.c1=as.vector(scale(as.numeric(model.data.lateral_approach$condition==levels(as.factor(model.data.lateral_approach$condition))[2]), center=TRUE, scale= FALSE))
model.data.lateral_approach$condition.c2=as.vector(scale(as.numeric(model.data.lateral_approach$condition==levels(as.factor(model.data.lateral_approach$condition))[3]), center=TRUE, scale= FALSE))
model.data.lateral_approach$sex<- as.factor(model.data.lateral_approach$sex)


model.data.lateral_approach$prop.duration.scaled <- (model.data.lateral_approach$prop.duration*(length(model.data.lateral_approach$prop.duration) - 1) + 0.5)/length(model.data.lateral_approach$prop.duration)#transform DV to exclude 0 and 1s
```


```{r}
library(glmmTMB)
m1.lateral.approach<-glmmTMB(prop.duration.scaled ~ condition + z.trial + z.order + z.age + sex+(1+(condition.c1+condition.c2)+z.trial+z.order|subject), family=beta_family, data=model.data.lateral_approach,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))
#convergence issues

#fit the model without the correlations between random intercept and random slopes
m1.lateral.approach<-glmmTMB(prop.duration.scaled ~ condition + z.trial + z.order + z.age + sex+(1|subject)+(0+condition.c1|subject)+(0+condition.c2|subject)+(0+z.trial|subject)+(0+z.order|subject), family=beta_family, data=model.data.lateral_approach,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

overdisp.test(m1.lateral.approach)

```
```{r}
drop1_m1.lateral_approach<-drop1(m1.lateral.approach, test="Chisq")%>%add_row(Df = rep(NA,1),  .before = 3)
```

```{r}
summary(m1.lateral.approach)
```


```{r}
model.data.lateral_approach$condition.relevelled<-relevel(model.data.lateral_approach$condition, ref = "teasing")
levels(model.data.lateral_approach$condition.relevelled)
model.data.lateral_approach$condition.rl.c1=as.vector(scale(as.numeric(model.data.lateral_approach$condition.relevelled==levels(as.factor(model.data.lateral_approach$condition.relevelled))[2]), center=TRUE, scale= FALSE))
model.data.lateral_approach$condition.rl.c2=as.vector(scale(as.numeric(model.data.lateral_approach$condition.relevelled==levels(as.factor(model.data.lateral_approach$condition.relevelled))[3]), center=TRUE, scale= FALSE))


m1.lateral.approach.relevelled<-glmmTMB(prop.duration.scaled ~ condition.relevelled + z.trial + z.order + z.age + sex+(1|subject)+(0+condition.rl.c1|subject)+(0+condition.rl.c2|subject)+(0+z.trial|subject)+(0+z.order|subject), family=beta_family, data=model.data.lateral_approach,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

summary(m1.lateral.approach.relevelled)
```


model stability
```{r}

m1.stab.lateral.approach=glmmTMB.stab(model.res=m1.lateral.approach, para=F, data=model.data.lateral_approach)

m1.stab.lateral.approach$summary

m.stab.plot(round(m1.stab.lateral.approach$summary[, -1], 3))
```



```{r}
library(car)
xx=lm(prop.duration.scaled ~ condition + z.trial + z.order + z.age + sex, data=model.data.lateral_approach)
vif(xx)
```


```{r}
boot.m1.lateral.approach<-boot.glmmTMB(m1.lateral.approach, data=model.data.lateral_approach,
nboots=1000, para=T, n.cores=3, resol=100, level=0.95)
```



### output table

```{r}

model_table_lateral_approach<- bind_cols(as.data.frame(summary(m1.lateral.approach)$coefficients$cond),
                             boot.m1.lateral.approach$ci.estimates$fe[1:7,],
                             drop1_m1.lateral_approach) %>%
                             select(Estimate, SE = `Std. Error`,LowerCI = X2.5., UpperCI = X97.5., z=`z value`, p=`Pr(>|z|)`,  Chi2 = LRT, df = Df, p_LRT = `Pr(>Chi)`) %>%
  mutate(across(.cols = c(p, p_LRT), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:z, Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
 # mutate(across(Chi2:p_LRT, ~replace_na(.x, "")))%>%
mutate(p_LRT=replace(p_LRT, p_LRT==0.000, "<0.001"))%>%
mutate(p=replace(p, p==0.000, "<0.001"))

write.csv(model_table_lateral_approach, file = "saves/m1_results_lateral_approach.csv")
```








#### Plots

```{r}
walk.away.data$condition<-fct_relevel(as.factor(walk.away.data$condition), "blocked", "teasing", "clumsy")
walk.away.data$condition2 <- jitter(as.numeric(as.factor(walk.away.data$condition), amount = .0001))

library(gghalves)


away_plot <- ggplot(data = walk.away.data, aes(x = condition, y= mean_prop_away_time, group=condition)) +
      geom_line(aes(x = condition2, group = subject), color = "darkgray", lty = 1, alpha = .3) +
  geom_point(data = walk.away.data %>% filter(condition == "blocked"), aes(x = condition2), color = "dodgerblue", size = 1.5, alpha = .5) +
  geom_point(data = walk.away.data %>% filter(condition == "clumsy"), aes(x = condition2), color = "darkorange", size = 1.5, alpha = .5, ) +
    geom_point(data = walk.away.data %>% filter(condition == "teasing"), aes(x = condition2), color = "darkgreen", size = 1.5, alpha = .5, ) +
     geom_half_boxplot(
     data = walk.away.data %>% filter(condition == "blocked"), aes(x = condition2, y = mean_prop_away_time), position = position_nudge(x = 2.3), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'dodgerblue', alpha = .5) +
   
   geom_half_boxplot(
     data = walk.away.data %>% filter(condition == "clumsy"), aes(x = condition2, y = mean_prop_away_time), position = position_nudge(x = 0.8), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkorange', alpha = .5) +
  
     geom_half_boxplot(
     data = walk.away.data %>% filter(condition == "teasing"), aes(x = condition2, y = mean_prop_away_time), position = position_nudge(x = 1.55), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkgreen', alpha = .5) +

  # Define additional settings
  xlab("Condition") +
  ylab("Proportion time away") +
  scale_x_continuous(breaks = c(1, 2, 3), labels = c("Blocked", "Teasing", "Clumsy"), limits = c(0.75,4)) +
  ylim(0, 1) +
  theme_classic()

away_plot 

ggsave(away_plot , filename = "graphs/unwilling_unable_away_time.png", width = 8, height = 8, scale = 0.4)

```


Look away
```{r}
look.data$condition<-fct_relevel(as.factor(look.data$condition), "blocked", "teasing", "clumsy")
look.data$condition2 <- jitter(as.numeric(as.factor(look.data$condition), amount = .0001))

library(gghalves)


look_away_plot <- ggplot(data = look.data, aes(x = condition, y= mean_look_away, group=condition)) +
      geom_line(aes(x = condition2, group = subject), color = "darkgray", lty = 1, alpha = .3) +
  geom_point(data = look.data %>% filter(condition == "blocked"), aes(x = condition2), color = "dodgerblue", size = 1.5, alpha = .4) +
  geom_point(data = look.data %>% filter(condition == "clumsy"), aes(x = condition2), color = "darkorange", size = 1.5, alpha = .4, ) +
    geom_point(data = look.data %>% filter(condition == "teasing"), aes(x = condition2), color = "darkgreen", size = 1.5, alpha = .4, ) +
     geom_half_boxplot(
     data = look.data %>% filter(condition == "blocked"), aes(x = condition2, y = mean_look_away), position = position_nudge(x = 2.3), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'dodgerblue', alpha = .5) +
   
   geom_half_boxplot(
     data = look.data %>% filter(condition == "clumsy"), aes(x = condition2, y = mean_look_away), position = position_nudge(x = 0.8), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkorange', alpha = .5) +
  
     geom_half_boxplot(
     data = look.data %>% filter(condition == "teasing"), aes(x = condition2, y = mean_look_away), position = position_nudge(x = 1.55), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkgreen', alpha = .5) +
  # Define additional settings
  xlab("Condition") +
  ylab("Proportion looking away") +
  scale_x_continuous(breaks = c(1, 2, 3), labels = c("Blocked", "Teasing", "Clumsy"), limits = c(0.75,4)) +
  ylim(0, 1) +
  theme_classic()

look_away_plot 

ggsave(look_away_plot , filename = "graphs/unwilling_unable_look_away_time.png", width = 8, height = 8, scale = 0.4)

```


Rest (sitting / lying down)
```{r}
rest.data$condition<-fct_relevel(as.factor(rest.data$condition), "blocked", "teasing", "clumsy")

rest.data$condition2 <- jitter(as.numeric(as.factor(rest.data$condition), amount = .0001))

library(gghalves)


rest_plot <- ggplot(data = rest.data, aes(x = condition, y= mean_prop_rest, group=condition)) +
      geom_line(aes(x = condition2, group = subject), color = "darkgray", lty = 1, alpha = .3) +
  geom_point(data = rest.data %>% filter(condition == "blocked"), aes(x = condition2), color = "dodgerblue", size = 1.5, alpha = .5) +
  geom_point(data = rest.data %>% filter(condition == "clumsy"), aes(x = condition2), color = "darkorange", size = 1.5, alpha = .5, ) +
    geom_point(data = rest.data %>% filter(condition == "teasing"), aes(x = condition2), color = "darkgreen", size = 1.5, alpha = .5, ) +
     geom_half_boxplot(
     data = rest.data %>% filter(condition == "blocked"), aes(x = condition2, y = mean_prop_rest), position = position_nudge(x = 2.3), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'dodgerblue', alpha = .5) +
   
   geom_half_boxplot(
     data = rest.data %>% filter(condition == "clumsy"), aes(x = condition2, y = mean_prop_rest), position = position_nudge(x = 0.8), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkorange', alpha = .5) +
  
     geom_half_boxplot(
     data = rest.data %>% filter(condition == "teasing"), aes(x = condition2, y = mean_prop_rest), position = position_nudge(x = 1.55), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkgreen', alpha = .5) +
    # Define additional settings
  xlab("Condition") +
  ylab("Proportion time sitting / lying down") +
  scale_x_continuous(breaks = c(1, 2, 3), labels = c("Blocked", "Teasing", "Clumsy"), limits = c(0.75,4)) +
  ylim(0, 1) +
  theme_classic()

rest_plot 

ggsave(rest_plot , filename = "graphs/unwilling_unable_rest_time.png", width = 8, height = 8, scale = 0.4)

```


Lateral approach
```{r}
lateral.approach.data$condition<-fct_relevel(as.factor(lateral.approach.data$condition), "blocked", "teasing", "clumsy")

lateral.approach.data$condition2 <- jitter(as.numeric(as.factor(lateral.approach.data$condition), amount = .0001))

library(gghalves)


lat_plot <- ggplot(data = lateral.approach.data, aes(x = condition, y= mean_prop_lateral_approach, group=condition)) +
      geom_line(aes(x = condition2, group = subject), color = "darkgray", lty = 1, alpha = .3) +
  geom_point(data = lateral.approach.data %>% filter(condition == "blocked"), aes(x = condition2), color = "dodgerblue", size = 1.5, alpha = .5) +
  geom_point(data = lateral.approach.data %>% filter(condition == "clumsy"), aes(x = condition2), color = "darkorange", size = 1.5, alpha = .5, ) +
    geom_point(data = lateral.approach.data %>% filter(condition == "teasing"), aes(x = condition2), color = "darkgreen", size = 1.5, alpha = .5, ) +
     geom_half_boxplot(
     data = lateral.approach.data %>% filter(condition == "blocked"), aes(x = condition2, y = mean_prop_lateral_approach), position = position_nudge(x = 2.3), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'dodgerblue', alpha = .5) +
      geom_half_boxplot(
     data = lateral.approach.data %>% filter(condition == "clumsy"), aes(x = condition2, y = mean_prop_lateral_approach), position = position_nudge(x = 0.8), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkorange', alpha = .5) +
       geom_half_boxplot(
     data = lateral.approach.data %>% filter(condition == "teasing"), aes(x = condition2, y = mean_prop_lateral_approach), position = position_nudge(x = 1.55), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .05, 
     fill = 'darkgreen', alpha = .5) +
    # Define additional settings
  xlab("Condition") +
  ylab("Proportion time lateral approach") +
  scale_x_continuous(breaks = c(1, 2, 3), labels = c("Blocked", "Teasing", "Clumsy"), limits = c(0.75,4)) +
  ylim(0, 1) +
  theme_classic()

lat_plot 

ggsave(lat_plot , filename = "graphs/unwilling_unable_lat_prop.png", width = 8, height = 8, scale = 0.4)

```

```{r}
library(cowplot)

pg<-plot_grid(away_plot, look_away_plot, rest_plot, lat_plot, nrow=2, labels=c("A", "B", "C", "D"))

ggsave(pg, filename = "graphs/unwilling_unable_plot_grid.jpg", height = 15, width=16, scale=0.46)

ggsave(pg, filename = "graphs/unwilling_unable_plot_grid.pdf", height = 15, width=16, scale=0.46)
```


```{r}
save.image("unwilling_unable_analysis.RData")
```


##### Reli analysis

Load reli data
```{r}
reli.data <- read.csv(file = "data/unwilling_unable_scoring_data_reli.csv")
reli.dog.data <- read.csv(file = "data/unwilling_unable_reli_dogs.csv")

view(dfSummary(reli.data))
table(reli.data$subject, reli.data$trial)
table(reli.data$subject, reli.data$condition)

```

aggregating data per trial

```{r}
reli.agg.data<-reli.data %>%
  mutate(Value=fct_recode(as.factor(Value), "rest"="sitting_down", "rest"="laying_down"))%>%
  mutate(look_away=ifelse(Value=="look_away", 1, NA))%>%
  group_by(subject, condition, trial, Behaviour, Value)%>%
  summarise(sum_duration=sum(duration), look_away=sum(look_away))%>%
  ungroup()%>%
  droplevels()%>%
  complete(subject, condition,  trial, Value, fill=list(sum.duration=0))%>% #fill in 0s
  complete(subject, condition, trial, Value, fill=list(look_away=0))%>%
  inner_join(reli.dog.data)%>%
  left_join(demo.data)%>%
  rename(sex=gender)%>%
  replace_na(list(sum_duration=0))%>%
  rename(sum_duration_reli=sum_duration, look_away_reli=look_away)
view(dfSummary(reli.agg.data))

reli.trial.duration<-reli.agg.data%>%
  filter(Behaviour=="trial")%>%
  rename(trial_duration_reli=sum_duration_reli)%>%
  select(-Behaviour, -Value)



reli.prop.data<-reli.agg.data%>%
   filter(Value!="1", Value!="2", Value!="3", Value!="4")%>%
  full_join(reli.trial.duration)%>%
  mutate(reli.prop.duration=sum_duration_reli/trial_duration_reli)


```
time away
```{r}
reli.away.data<-reli.prop.data%>%
    filter(Value=="walk_away")%>%
  select(-Behaviour)%>%
  inner_join(model.data.away%>%select(-Behaviour))

cor.test(reli.away.data$reli.prop.duration ,reli.away.data$prop.duration, method = "spearman", use ="complete.obs")

```
resting
```{r}
reli.rest.data<-reli.prop.data%>%
    filter(Value=="rest")%>%
  select(-Behaviour)%>%
  inner_join(model.data.rest%>%select(-Behaviour))

cor.test(reli.rest.data$reli.prop.duration ,reli.rest.data$prop.duration, method = "spearman", use ="complete.obs")

```
look away:
```{r}

reli.look.data<-reli.prop.data%>%
    filter(Value=="look_away")%>%
    mutate(look_away_binary_reli=ifelse(look_away_reli>0,1,ifelse(look_away_reli==0, 0, NA)))%>%
  select(-Behaviour)%>%
  inner_join(model.data.look%>%select(-Behaviour))%>%
  mutate(match=ifelse(look_away_binary_reli==look_away_binary, 1, 0))

library(psych)
cohen.kappa(cbind(reli.look.data$look_away_binary_reli,reli.look.data$look_away_binary))


mean(reli.look.data$match)

```

```{r}

reli.lateral.data<-reli.prop.data%>%
    filter(Value=="lateral_approach")%>%
    select(-Behaviour)%>%
  inner_join(model.data.lateral_approach%>%select(-Behaviour))

cor.test(reli.lateral.data$reli.prop.duration ,reli.lateral.data$prop.duration, method = "spearman", use ="complete.obs")


```

